\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\title{Big Data Initiative}
\author{Atabak Hafeez}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
\section{Big Data Initiative: Why effective caching on online videos is important relative to Big Data?}

Caching is very important when it comes to streaming videos online. According to an article (1), in 2007, 50\% traffic came from several thousand sites and by 2009, 50\% traffic came from 150 sites. Furthermore, by 2013, the 50\% of all internet traffic came form 35 or more sites. From this we can see that the traffic of websites that are popular is being aggravated. A lot of this increase in traffic to a smaller number of websites is due to online video streaming.

Before 2012, video streaming was done using using Real Time Messaging Protocol (RTMP)-based servers. This requires a streaming server and a near-continuous connection between the server and player. Requiring a streaming server can increase implementation cost, while RTMP-based packets can be blocked by firewalls. In 2012, this was replaced by an (Hypertext Transfer Protocol) HTTP-based servers known as MPEG DASH (Dynamic Adaptive Streaming over HTTP).  By using this technology, the servers were able to use HTTP-Caching. This latter capability decreased total bandwidth costs associated with delivering the video, since more data could be served from web-based caches rather than the origin server, and improved quality of service, since cached data is generally closer to the viewer and more easily retrievable.




(1) http://www.streamingmedia.com/Articles/Editorial/Featured-Articles/Online-Video-Jumps-on-the-Big-Data-Bandwagon-91353.aspx

(2) http://www.streamingmedia.com/Articles/Editorial/What-Is-.../What-is-MPEG-DASH-79041.aspx

%\subsection{}



\end{document}  